Data Analysis Methods for the Detection of the Epoch of Reionization

### 2017-07-17 PAPER.tex
-Elaborated on captions for Figures in Section 2 -Did a once-over read and edit of Section 2

\begin{center}
Power Spectrum Themes
\end{center}
\begin{itemize}
\item[] The accuracy and interpretation of a $21$ cm power spectrum can be encompassed in the following three themes.
\item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): As explained in the next section, certain analysis techniques can lead to the loss of the EoR signal. If not corrected for, it could lead to a false non-detection. Computing signal loss has subtle challenges but is crucial to the accuracy of any result.
\item \textbf{Error Bar Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on the $21$ cm power spectrum result determine the difference between a detection and a null result, which have two very different implications. Errors can be estimated in a variety of ways, and we will discuss a few of them.
\item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of bias in a visibility measurement that can leak its way into a power spectrum, such as bias from noise and foregrounds. Proving a bias is EoR may be the most difficult challenge for $21$ cm analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR. In this paper we will highlight some sources of bias and discuss ways to mitigate its effects.
\end{itemize}

@@

where $\hat{\textbf{p}}$ is the normalized estimate of the true power spectrum . We compute $\textbf{M}$ using the Fisher matrix $\textbf{F}$, defined as:

@@

To build our intuition into how a particular choice of weighting, namely inverse covariance weighting, can lead to signal loss through the use of a toy model. Suppose we have a very simple dataset that contains 2-dimensional data (representing $100$ time integrations and $20$ frequency channels). This model represents realistic dimensions of about an hour of PAPER data which could be used for a power spectrum analysis. We create a mock bright foreground signal, $\textbf{x}_{FG}$, as a complex sinusoid that varies in time and frequency, as well as a mock EoR signal, $\textbf{x}_{EoR}$, as complex, random Gaussian noise. The sum of the two forms our combined data vector, $\textbf{x}$, to which we will be applying different weighting schemes. The three data vectors are shown on in Figure \ref{fig:toy_sigloss1}. Our ultimate goal in experimenting with weighting is to suppress the foregrounds perfectly without destroying EoR.

@@

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss1.png}
	\caption{Our toy model dataset contains a sinusoid foreground that varies in time and frequency and random Gaussian noise as a mock EoR signal. Real parts are shown here.}
	\label{fig:toy_sigloss1}
\end{figure}

@@

\begin{figure*}
	\centering
	\includegraphics[trim={0.3cm 0.2cm 1cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss3.png}
	\includegraphics[trim={1cm 0.2cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss4.png}
	\caption{Power spectrum of foregrounds only (blue), EoR only (red), and the combined dataset (green). Contrasted are the effect of using inverse covariance weighting (left) and projecting out the first eigenmode only (right).}
	\label{fig:toy_sigloss3}
\end{figure*}

As shown in Figure \ref{fig:toy_sigloss3}, our inverse covariance weighted result successfully suppresses foregrounds. This illustrates why inverse covariance weighting is attractive for $21$ cm data. It is also evident that our result fails to recover the EoR signal --- it exhibits the correct shape, but the amplitude level is slightly low. This is evidence of signal loss. In order to understand how this occurs, we need to closely study our covariance matrix, $\textbf{C}$.

@@

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss2.png}
	\caption{Eigenspectrum of foregrounds only (blue), EoR only (red), and FG + EoR (green).}
	\label{fig:toy_sigloss2}
\end{figure}

@@

Using what we've learned about the eigenspectrum, we can tweak it in a simple way to suppress foregrounds and yield zero signal loss. Namely, we can zero out all eigenmodes except the first one, thereby down-weighting the foregrounds perfectly and nothing else. The result is shown in the right plot of Figure \ref{fig:toy_sigloss3}. In this case, we perfectly recover EoR, demonstrating that if we can perfectly model our foregrounds, we can down-weight them without signal loss. However, this is not the case in reality since we aren't able to distinguish between foreground and EoR modes.

@@

A fringe-rate filter is an analysis technique designed to maximize sensitivity by integrating in time (\citealt{parsons_et_al2016}). To mimic this filter, we average every $4$ time integrations of our toy model dataset together, yielding $25$ independent samples in time (Figure \ref{fig:toy_sigloss5}, left). We choose these numbers so that the total number of independent samples is similar to the number of frequency channels (our matrices will be full rank). The resulting eigenspectra (Figure \ref{fig:toy_sigloss5}, right), as compared to those in Figure \ref{fig:toy_sigloss1}, fall more steeply for last few eigenmodes. This shape has large consequences on the resulting power spectra.

\begin{figure*}
	\centering
	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss5.png}
	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss6.png}
	\caption{Left: Our `fringe-rate filtered' toy model dataset. It contains $25$ independent samples in time. Real parts are shown here. Right: Eigenspectrum of foregrounds only (blue), EoR only (red), and both (green).}
	\label{fig:toy_sigloss5}
\end{figure*}

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss7.png}
	\caption{Power spectrum of foregrounds only (blue), EoR only (red), and the full inverse covariance weighted combined dataset (green) for a time-averaged dataset (fewer independent modes).}
	\label{fig:toy_sigloss7}
\end{figure}

@@

\begin{figure*}
	\centering
	\includegraphics[trim={0.4cm 0.8cm 1.3cm 1cm},clip,height=0.25\textwidth]{plots/toy_sigloss10.png}
	\includegraphics[trim={1cm 0.8cm 1.3cm 1cm},clip,height=0.25\textwidth]{plots/toy_sigloss8.png}
	\includegraphics[trim={0.4cm 0.8cm 1.3cm 1cm},clip,height=0.25\textwidth]{plots/toy_sigloss9.png}
	\includegraphics[trim={1cm 0.8cm 1.3cm 1cm},clip,height=0.25\textwidth]{plots/toy_sigloss11.png}
	\caption{Power spectra of foregrounds only (blue), EoR only (red), and the weighted combined dataset (green). We show four alternate weighting options that each avoid signal loss, including modeling the covariance matrix of EoR (upper left), regularizing $\textbf{C}$ by adding an identity matrix to it (upper right), using only the first few eigenmodes of $\textbf{C}$ (lower left), and multiplying an identity matrix to $\textbf{C}$ (lower right).}
	\label{fig:toy_sigloss8}
\end{figure*}

@@

In summary, we have a choice of how to weight $21$ cm data. Ideally, we want to down-weight bright foregrounds without removing the underlying cosmological signal. Inverse covariance weighting is an optimal weighting for dealing with foregrounds, but its aggressiveness results in sloped eigenspectra shapes, the overfitting of noise, and thus signal loss. The application of a fringe-rate filter heightens this effect by reducing the number of independent samples and steepening eigenspectra further. Rather than use inverse covariance weighting, there are several alternate ways to regularize covariance matrices and flatten out eigenspectra to minimize signal loss. In Section \ref{sec:Sigloss}, we apply the lessons we've learned about signal loss and its interaction with fringe-rate filtering and inverse covariance weighting to PAPER-64 data.

@@

A common technique used to estimate the variance in a dataset is bootstrapping. Bootstrapping is a metric that relies on sampling with replacement and allows the estimation of a sampling distribution. For example, power spectrum measurements of $21$ cm data can be made along many axes, including time and baselines. Through the process of bootstrapping, we can obtain error bars for our results which represent the underlying distribution of power spectra values that are allowed by our measurements.

@@

One major caveat of bootstrapping is that the method is no longer valid when working with correlated data. In other words, bootstrapping assumes completely independent samples. Therefore, the use of a fringe-rate filter, which averages data in time to increase sensitivity, creates a situation in which bootstrapping can under-estimate errors.

@@

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error1.png}
	\caption{Error estimation produced by bootstrapping as a function of the number of samples drawn when sampling with replacement. The grey star represents the error associated with drawing $1000$ samples from a length $1000$ array of random noise. The black points correspond to time-averaged data and illustrate how errors can be underestimated if drawing more samples than independent ones in the data. There are $100$ independent samples in the time-averaged data and using this number does indeed match the theoretical error prediction.}
	\label{fig:toy_error1}
\end{figure}

@@

It is clear that the fraction of independent baselines in a group is always greater using our new sampling approach, with the greatest discrepancy for small number of groups (large number of baselines per group). An analog for the y-axis in Figure \ref{fig:toy_error2} is the final power spectrum sensitivity in temperature-squared space, which decreases as the square root of the number of baselines that are averaged together for a measurement.

In summary, bootstrapping is still an effective and straightforward way to estimate errors of a dataset. However, one must be careful about violating independence assumptions, as it is possible to under-estimate errors by over-sampling data. Additionally, small changes in the way datasets are randomly sampled can ensure that the overall sensitivity is maximized.

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error2.png}
	\caption{Fraction of independent baselines in a baseline group as a function of the number of baselines in a group. A fraction of $1.0$ means that all baselines in a group are independent, and therefore sensitivity is maximized (alternatively, this axis can be treated as a power spectrum sensitivity in temperature-squared space). Two bootstrapping methods are shown here --- sampling all elements with replacement (grey) and sampling only the last element with replacement (black). The former over-estimates error bars by not maximizing baseline sensitivity to its full capacity.}
	\label{fig:toy_error2}
\end{figure}

@@

Another way of introducing a noise bias into data is via cross-talk subtraction. Cross-talk is caused by the cross-coupling of signals between antennas and shows up as a constant bias in time in visibilities. For PAPER-64, cross-talk is removed during redundant calibration, when the deviation from an average visibility (across similar baseline types) is subtracted off of each visibility. This type of removal preserves signals common to all baselines, such as the EoR signal, but also has the consequence of introducing a low level bias. This bias term comes from the averaged cross-talk across a redundant baseline group and hence every baseline now has a piece of all the other baseline's (of the same type) noise. One way to remove this noise bias is with the use of a fringe-rate filter, which can be chosen to filter out static signals (filter out zero `fringe-rates').

@@

One last source of foreground bias that we will highlight here is polarization leakage. When forming Stokes I from $XX$ and $YY$ polarization visibility data, we ignore the beam asymmetry between the two. This mismatch can cause leakage from Stokes Q ($V_{Q} = \frac{1}{2}(V_{XX}-V_{YY})$) into Stokes I ($V_{I} = \frac{1}{2}(V_{XX}+V_{YY})$). Another way of describing this leakage is that Faraday Rotation, which causes a rotation of the polarization angle of a signal, can induce spectral structure at certain delays (\citealt{moore_et_al2013}). This type of sky bias is dependent on rotation measures, which characterize the amount of polarization rotation. If a particular rotation measure is such that a Stokes Q signal ends up falling at a power spectrum delay of interest, the Stokes I result would be biased.

One preventative measure for polarization leakage could be tailoring a fringe-rate filter in a way that improves the match between $XX$ and $YY$ polarization beams (\citealt{parsons_et_al2016}). There are also multiple ways of tracing a power spectrum detection to a polarization bias. One can look at Stokes Q power spectra to estimate the amount of expected leakage (\citealt{moore_et_al2013}). In addition, jack-knife tests can be used to investigate whether polarization leakage affects a result. For example, rotation measures are highest when observing into the Galactic plane due to increased Faraday rotation (\cc{citation?}), so one could imagine looking at different rotation measure bins along the Galactic latitude axis in order to identify whether a strong rotation measure coincides with a particular power spectrum detection.

>>>>

\begin{center}
Power Spectrum Themes
\end{center}
\begin{itemize}
\item[] The accuracy and interpretation of a $21$ cm power spectrum can be encompassed in the following three themes.
\item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): As explained in the next section, certain analysis techniques can lead to the loss of the EoR signal. If not corrected for, it could lead to a false non-detection. Computing signal loss has subtle challenges but is crucial to the accuracy of any result.
\item \textbf{Error Bar Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on the $21$ cm power spectrum result determine the difference between a detection and a null result, which have two very different implications. Errors can be estimated in a variety of ways, and we will discuss a few of them.
\item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of bias in a visibility measurement that can leak its way into a power spectrum, such as bias from noise and foregrounds. Proving a bias is EoR may be the most difficult challenge for $21$ cm analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR. In this paper we will highlight some sources of bias and discuss ways to mitigate their effects.
\end{itemize}

@@

where $\hat{\textbf{p}}$ is the normalized estimate of the true power spectrum. We compute $\textbf{M}$ using the Fisher matrix $\textbf{F}$, defined as:

@@

To build our intuition into how a particular choice of weighting, namely inverse covariance weighting, can lead to signal loss, we use a toy model. Suppose we have a very simple dataset that contains 2-dimensional data (representing $100$ time integrations and $20$ frequency channels). This model represents realistic dimensions of about an hour of PAPER data which could be used for a power spectrum analysis. We create a mock bright foreground signal, $\textbf{x}_{FG}$, as a complex sinusoid that varies in time and frequency, as well as a mock EoR signal, $\textbf{x}_{EoR}$, as complex, random Gaussian noise. The sum of the two forms our combined data vector, $\textbf{x}$, to which we will be applying different weighting schemes. The three data vectors are shown in Figure \ref{fig:toy_sigloss1}. Our ultimate goal in experimenting with weighting is to suppress the foregrounds perfectly without destroying EoR.

@@

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss1.png}
	\caption{Our toy model dataset contains a sinusoid foreground that varies in time and frequency and random Gaussian noise as a mock EoR signal. Real parts are shown here. \cc{colorbar?}}
	\label{fig:toy_sigloss1}
\end{figure}

@@

\begin{figure*}
	\centering
	\includegraphics[trim={0.3cm 0.2cm 1cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss3.png}
	\includegraphics[trim={1cm 0.2cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss4.png}
	\caption{Resulting power spectrum estimates for our toy model simulation --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green). We use inverse covariance weighting where $\textbf{C}$ is derived from the data (left), contrasted with projecting out the first eigenmode only (right). There is signal loss for the former but not the latter.}
	\label{fig:toy_sigloss3}
\end{figure*}

As shown in Figure \ref{fig:toy_sigloss3} (left plot), our inverse covariance weighted result successfully suppresses foregrounds. This illustrates why inverse covariance weighting is attractive for $21$ cm data. It is also evident that our result fails to recover the EoR signal --- it exhibits the correct shape, but the amplitude level is slightly low. This is evidence of signal loss. In order to understand how this occurs, we need to closely study our covariance matrix, $\textbf{C}$.

@@

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss2.png}
	\caption{Eigenspectrum of foregrounds only (blue), EoR only (red), and FG + EoR (green). The eigenspectrum of foregrounds only peaks at the zeroth eigenmode, a consequence of the presence of only one sinusoid. All eigenspectra steepen slightly for the final few eigenmodes, a behavior that results in some modes being upweighted more strongly than others, thereby overfitting noise and causing signal loss in the final power spectrum estimate (Figure \ref{fig:toy_sigloss3}, left). If only the first eigenmode is used, all others get equal weights and hence, there is no signal loss (Figure \ref{fig:toy_sigloss3}, right)}
	\label{fig:toy_sigloss2}
\end{figure}

@@

Using what we've learned about the eigenspectrum, we can tweak it in a simple way to suppress foregrounds and yield zero signal loss. Namely, we can project out the zeroth eigenmode (i.e. zero out all eigenmodes except the first one), thereby down-weighting the foregrounds perfectly and nothing else. The result is shown in the right plot of Figure \ref{fig:toy_sigloss3}. In this case, we perfectly recover EoR, demonstrating that if we can perfectly model our foregrounds, we can down-weight them without signal loss. However, this is not the case in reality since we aren't able to distinguish between foreground and EoR modes.

@@

A fringe-rate filter is an analysis technique designed to maximize sensitivity by integrating in time (\citealt{parsons_et_al2016}). To mimic this filter, we average every $4$ time integrations of our toy model dataset together, yielding $25$ independent samples in time (Figure \ref{fig:toy_sigloss5}, left). We choose these numbers so that the total number of independent samples is similar to the number of frequency channels --- therefore, our matrices will be full rank. The resulting eigenspectra (Figure \ref{fig:toy_sigloss5}, right), as compared to those in Figure \ref{fig:toy_sigloss2}, fall more steeply for the last few eigenmodes. This shape has large consequences on the resulting power spectra.

\begin{figure*}
	\centering
	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss5.png}
	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss6.png}
	\caption{Left: Our `fringe-rate filtered' (time-averaged) toy model dataset. It contains $25$ independent samples in time. Real parts are shown here. Right: Eigenspectrum of the covariance matrices of foregrounds only (blue), EoR only (red), and FG + EoR (green). The eigenspectrum of foregrounds only peaks at the zeroth eigenmode, a consequence of the presence of only one sinusoid. All eigenspectra steepen for the final few eigenmodes, a behavior that results in a few noisy modes being upweighted more strongly than others, thereby overfitting noise and causing signal loss in the final power spectrum estimate.}
	\label{fig:toy_sigloss5}
\end{figure*}

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss7.png}
	\caption{Resulting power spectrum estimate for our fringe-rate filtered toy model simulation --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green). We use inverse covariance weighting where $\textbf{C}$ is derived from the data. There is a larger amount of signal loss than un-fringe-rate filtered data. The power spectrum estimate is also noisier, since most of the information used in constructing the estimate came from only a few eigenmodes.}
	\label{fig:toy_sigloss7}
\end{figure}

@@

\begin{figure*}
	\centering
	\includegraphics[trim={0.4cm 0.8cm 1.3cm 1cm},clip,height=0.25\textwidth]{plots/toy_sigloss10.png}
	\includegraphics[trim={1cm 0.8cm 1.3cm 1cm},clip,height=0.25\textwidth]{plots/toy_sigloss8.png}
	\includegraphics[trim={0.4cm 0.8cm 1.3cm 1cm},clip,height=0.25\textwidth]{plots/toy_sigloss9.png}
	\includegraphics[trim={1cm 0.8cm 1.3cm 1cm},clip,height=0.25\textwidth]{plots/toy_sigloss11.png}
	\caption{Resulting power spectra estimates for our fringe-rate filtered toy model simulation --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green). We show four alternate weighting options that each avoid signal loss, including modeling the covariance matrix of EoR (upper left), regularizing $\textbf{C}$ by adding an identity matrix to it (upper right), using only the first three eigenmodes of $\textbf{C}$ (lower left), and multiplying an identity matrix to $\textbf{C}$ (lower right). There are many regularization options available to minimize signal loss, and some work better than others depending on the dataset.}
	\label{fig:toy_sigloss8}
\end{figure*}

@@

In summary, we have a choice of how to weight $21$ cm data. Ideally, we want to down-weight bright foregrounds without removing the underlying cosmological signal. Inverse covariance weighting is an optimal weighting scheme for dealing with foregrounds, but its aggressiveness results in sloped eigenspectra shapes, the overfitting of noise, and thus signal loss. The application of a fringe-rate filter heightens this effect by reducing the number of independent samples and steepening eigenspectra further. Rather than use inverse covariance weighting, there are several alternate ways to regularize covariance matrices and flatten out eigenspectra to minimize signal loss. In Section \ref{sec:Sigloss}, we apply the lessons we've learned about signal loss and its interaction with fringe-rate filtering and inverse covariance weighting to PAPER-64 data.

@@

A common technique used to estimate the variance in a dataset is bootstrapping. Bootstrapping is a metric that relies on sampling with replacement and allows the estimation of a sampling distribution. For example, power spectrum measurements of $21$ cm data can be made along many axes, including time and baselines. Through the process of bootstrapping along these axes, we can obtain error bars for our results which represent the underlying distribution of power spectra values that are allowed by our measurements.

@@

One major caveat of bootstrapping is that the method is no longer valid when working with correlated data. In other words, bootstrapping assumes completely independent samples. Therefore, the use of a fringe-rate filter, which averages data in time to increase sensitivity, creates a situation in which bootstrapping can under-estimate errors. We will now show this effect using our toy model.

@@

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error1.png}
	\caption{Power spectrum error estimation produced by bootstrapping as a function of the number of samples drawn when sampling with replacement. The grey star represents the error associated with drawing $1000$ samples from a length $1000$ array of random noise. The black points correspond to time-averaged data and illustrate how errors can be underestimated if drawing more samples than independent ones in the data. There are $100$ independent samples in the time-averaged data --- hence, using this number does indeed match the theoretical error prediction.}
	\label{fig:toy_error1}
\end{figure}

@@

It is clear that the fraction of independent baselines in a group is always greater using our revised sampling approach, with the greatest discrepancy for small number of groups (large number of baselines per group). The more baselines per group, the more sensitivity we can gain by ensuring that most of the baselines are independent ones. An analog for the y-axis in Figure \ref{fig:toy_error2} is therefore the final power spectrum sensitivity in temperature-squared space, which decreases as the square root of the number of baselines that are averaged together for a measurement.

In summary, bootstrapping is still an effective and straightforward way to estimate errors of a dataset. However, one must be careful about violating independence assumptions, as it is possible to under-estimate errors by over-sampling data. Additionally, small changes in the way a dataset is randomly sampled can ensure that its overall sensitivity is maximized.

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error2.png}
	\caption{Fraction of independent baselines in a baseline group as a function of the number of baselines in a group. A fraction of $1.0$ means that all baselines in a group are independent, and therefore sensitivity is maximized (alternatively, this axis can be treated as a power spectrum sensitivity in temperature-squared space). Two bootstrapping methods are shown here --- sampling all elements with replacement (grey) and sampling only the last element with replacement (black). The former over-estimates error bars since some baselines end up being repeated due to random sampling. Therefore, baseline sensitivity is not maximized to its full capacity.}
	\label{fig:toy_error2}
\end{figure}

@@

Another way of introducing a noise bias into data is via cross-talk subtraction. Cross-talk is caused by the cross-coupling of signals between antennas and shows up as a constant bias in time in visibilities. For PAPER-64, cross-talk is removed during redundant calibration, when the deviation from an average visibility (across similar baseline types) is subtracted off of each visibility. This type of removal preserves signals common to all baselines, such as the EoR signal, but also has the consequence of introducing a low level bias. This bias term comes from the averaged cross-talk across a redundant baseline group and hence every baseline has a piece of all the other baseline's (of the same type) noise. One way to remove this noise bias is with the use of a fringe-rate filter, which can be chosen to filter out static signals (i.e. filter out zero `fringe-rates').

@@

One last source of foreground bias that we will highlight here is polarization leakage. When forming Stokes I from $XX$ and $YY$ polarization visibility data, we ignore the beam asymmetry between the two. This mismatch can cause leakage from Stokes Q ($V_{Q} = \frac{1}{2}(V_{XX}-V_{YY})$) into Stokes I ($V_{I} = \frac{1}{2}(V_{XX}+V_{YY})$). Another way of describing this leakage is that Faraday Rotation, which causes a rotation of the polarization angle of a signal, can induce spectral structure at certain delays (\citealt{moore_et_al2013}). This type of sky bias is dependent on rotation measures, which characterize the amount of polarization rotation. If a particular rotation measure is such that a Stokes Q signal ends up falling at a power spectrum delay of interest, the Stokes I result for that $k$ would be biased.

One preventative measure for polarization leakage could be tailoring a fringe-rate filter in a way that improves the match between $XX$ and $YY$ polarization beams (\citealt{parsons_et_al2016}). There are also multiple ways of tracing a power spectrum detection to a polarization bias. One can look at Stokes Q power spectra to estimate the amount of expected leakage (\citealt{moore_et_al2013}). In addition, jack-knife tests can be used to investigate whether polarization leakage affects a result. For example, rotation measures are highest when observing into the Galactic plane due to increased Faraday rotation (\cc{citation?}), so one could imagine looking at different rotation measure bins along the Galactic latitude axis in order to identify whether a strong rotation measure coincides with a particular power spectrum bias.
